---
title: "Data Anaylsis: McNemar's Test"
output:
  html_document :
    theme: flatly
    toc: FALSE
---

<br>

---

## Introduction 
This markdown conducts a McNemar's test for each question and calculates/interprets Cohen's g.
    
---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* effectsize: for interpreting Cohen's g

```{r libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here) #to set the path
library(effectsize) #to interpret Cohen's g

#for reproducibility
set.seed(123)
```

---

## Load Data
Load the data saved in the `raw_data` folder.

```{r load data}
#define path to data
data_location <- here::here("data", "processed_data", "processeddata.rds")

#load data
data <- readRDS(data_location)

```

---

## Data Overview
Look at the data to ensure variables imported correctly.

```{r data overview}
#data overview
summary(data)

```

---

## McNemar's Test for Each Question

```{r McNemar Test}
#Q1 table
table(data$Q1_PRE, data$Q1_POST)

#Q1 test
mcnemar.test(table(data$Q1_PRE, data$Q1_POST), correct = FALSE)

#Q2 table
table(data$Q2_PRE, data$Q2_POST)

#Q2 test
mcnemar.test(table(data$Q2_PRE, data$Q2_POST), correct = FALSE)

#Q3 table
table(data$Q3_PRE, data$Q3_POST)

#Q3 test
mcnemar.test(table(data$Q3_PRE, data$Q3_POST), correct = FALSE)

#Q4 table
table(data$Q4_PRE, data$Q4_POST)

#Q4 test
mcnemar.test(table(data$Q4_PRE, data$Q4_POST), correct = FALSE)

#Q5 table
table(data$Q5_PRE, data$Q5_POST)

#Q5 test
mcnemar.test(table(data$Q5_PRE, data$Q5_POST), correct = FALSE)

#Q6 table
table(data$Q6_PRE, data$Q6_POST)

#Q6 test
mcnemar.test(table(data$Q6_PRE, data$Q6_POST), correct = FALSE)

#Q7 table
table(data$Q7_PRE, data$Q7_POST)

#Q7 test
mcnemar.test(table(data$Q7_PRE, data$Q7_POST), correct = FALSE)

#Q8 table
table(data$Q8_PRE, data$Q8_POST)

#Q8 test
mcnemar.test(table(data$Q8_PRE, data$Q8_POST), correct = FALSE)

#Q9 table
table(data$Q9_PRE, data$Q9_POST)

#Q9 test
mcnemar.test(table(data$Q9_PRE, data$Q9_POST), correct = FALSE)

#Q10 table
table(data$Q10_PRE, data$Q10_POST)

#Q10 test
mcnemar.test(table(data$Q10_PRE, data$Q10_POST), correct = FALSE)

#Q11 table
table(data$Q11_PRE, data$Q11_POST)

#Q11 test
mcnemar.test(table(data$Q11_PRE, data$Q11_POST), correct = FALSE)

#Q12 table
table(data$Q12_PRE, data$Q12_POST)

#Q12 test
mcnemar.test(table(data$Q12_PRE, data$Q12_POST), correct = FALSE)

#Q13 table
table(data$Q13_PRE, data$Q13_POST)

#Q13 test
mcnemar.test(table(data$Q13_PRE, data$Q13_POST), correct = FALSE)

#Q14 table
table(data$Q14_PRE, data$Q14_POST)

#Q14 test
mcnemar.test(table(data$Q14_PRE, data$Q14_POST), correct = FALSE)
```

---

## Cohen's G for Each Question
```{r cohens g}
#Q1 cohens g
effectsize::cohens_g(data$Q1_PRE, data$Q1_POST, ci = 0.95, alternative = "two.sided")

#Q1 interpretation
effectsize::interpret_cohens_g(0.42)

#Q2 cohens g
effectsize::cohens_g(data$Q2_PRE, data$Q2_POST, ci = 0.95, alternative = "two.sided")

#Q2 interpretation
effectsize::interpret_cohens_g(0.45)

#Q3 cohens g
effectsize::cohens_g(data$Q3_PRE, data$Q3_POST, ci = 0.95, alternative = "two.sided")

#Q3 interpretation
effectsize::interpret_cohens_g(0.42)

#Q4 cohens g
effectsize::cohens_g(data$Q4_PRE, data$Q4_POST, ci = 0.95, alternative = "two.sided")

#Q4 interpretation
effectsize::interpret_cohens_g(0.32)

#Q5 cohens g
effectsize::cohens_g(data$Q5_PRE, data$Q5_POST, ci = 0.95, alternative = "two.sided")

#Q5 interpretation
effectsize::interpret_cohens_g(0.23)

#Q6 cohens g
effectsize::cohens_g(data$Q6_PRE, data$Q6_POST, ci = 0.95, alternative = "two.sided")

#Q6 interpretation
effectsize::interpret_cohens_g(0.08)

#Q7 cohens g
effectsize::cohens_g(data$Q7_PRE, data$Q7_POST, ci = 0.95, alternative = "two.sided")

#Q7 interpretation
effectsize::interpret_cohens_g(0.39)

#Q8 cohens g
effectsize::cohens_g(data$Q8_PRE, data$Q8_POST, ci = 0.95, alternative = "two.sided")

#Q8 interpretation
effectsize::interpret_cohens_g(0.46)

#Q9 cohens g
effectsize::cohens_g(data$Q9_PRE, data$Q9_POST, ci = 0.95, alternative = "two.sided")

#Q9 interpretation
effectsize::interpret_cohens_g(0.39)

#Q10 cohens g
effectsize::cohens_g(data$Q10_PRE, data$Q10_POST, ci = 0.95, alternative = "two.sided")

#Q10 interpretation
effectsize::interpret_cohens_g(0.47)

#Q11 cohens g
effectsize::cohens_g(data$Q11_PRE, data$Q11_POST, ci = 0.95, alternative = "two.sided")

#Q11 interpretation
effectsize::interpret_cohens_g(0.30)

#Q12 cohens g
effectsize::cohens_g(data$Q12_PRE, data$Q12_POST, ci = 0.95, alternative = "two.sided")

#Q12 interpretation
effectsize::interpret_cohens_g(0.19)

#Q13 cohens g
effectsize::cohens_g(data$Q13_PRE, data$Q13_POST, ci = 0.95, alternative = "two.sided")

#Q13 interpretation
effectsize::interpret_cohens_g(0.26)

#Q14 cohens g
effectsize::cohens_g(data$Q14_PRE, data$Q14_POST, ci = 0.95, alternative = "two.sided")

#Q14 interpretation
effectsize::interpret_cohens_g(0.38)

```

