---
title: "Data Anaylsis: Paired T-Test"
output:
  html_document :
    theme: flatly
    toc: FALSE
---

<br>

---

## Introduction 
This markdown conducts a paired sample t-test for the overall score as well as for the groups of questions.
    
---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* tidyverse: for using all packages in the Tidyverse for data wrangling (ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, and forcats)
* effectsize: for interpreting Cohen's g

```{r libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here) #to set the path
library(tidyverse) #to use all packages in the Tidyverse for data wrangling (ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, and forcats)
library(effectsize) #to interpret Cohen's g

#for reproducibility
set.seed(123)
```

---

## Load Data
Load the data saved in the `raw_data` folder.

```{r load data}
#define path to data
data_location <- here::here("data", "processed_data", "processeddata.rds")

#load data
data <- readRDS(data_location)

```

---

## Data Overview
Look at the data to ensure variables imported correctly.

```{r data overview}
#data overview
summary(data)

```

---

## Transform Data
We need to calculate the sums of the relevant categories:

Ebola 101: Q1 - Q3
EVD Monitoring: Q4 - Q6
The Infectious Disease Network: Q7 - Q10

```{r transform data}
#ebola 101
data$Ebola_PRE <- ((data$Q1_PRE + data$Q2_PRE + data$Q3_PRE)/3)*100
data$Ebola_POST <- ((data$Q1_POST + data$Q2_POST + data$Q3_POST)/3)*100

#evd monitoring
data$EVD_PRE <- ((data$Q4_PRE + data$Q5_PRE + data$Q6_PRE)/3)*100
data$EVD_POST <- ((data$Q4_POST + data$Q5_POST + data$Q6_POST)/3)*100

#IDN
data$IDN_PRE <- ((data$Q7_PRE + data$Q8_PRE + data$Q9_PRE + data$Q10_PRE)/4)*100
data$IDN_POST <- ((data$Q7_POST + data$Q8_POST + data$Q9_POST + data$Q10_POST)/4)*100

#convert score into percent
data$SCORE_PRE_PCT <- (data$SCORE_PRE/14)*100
data$SCORE_POST_PCT <- (data$SCORE_POST/14)*100
```

---

## Summary Stats
To calculate the mean and SD for each group of scores.
```{r summary stats}
#total score - pre
mean(data$SCORE_PRE_PCT)
sd(data$SCORE_PRE_PCT)

#total score - post
mean(data$SCORE_POST_PCT)
sd(data$SCORE_POST_PCT)

#ebola 101 - pre
mean(data$Ebola_PRE)
sd(data$Ebola_PRE)

#ebola 101 - post
mean(data$Ebola_POST)
sd(data$Ebola_POST)

#evd monitoring - pre
mean(data$EVD_PRE)
sd(data$EVD_PRE)

#evd monitoring - post
mean(data$EVD_POST)
sd(data$EVD_POST)

#idn - pre
mean(data$IDN_PRE)
sd(data$IDN_PRE)

#idn - post
mean(data$IDN_POST)
sd(data$IDN_POST)

```

---

## Paired t-test

```{r paired t test}
#overall score
t.test(data$SCORE_PRE_PCT, data$SCORE_POST_PCT, paired = TRUE)

#ebola 101
t.test(data$Ebola_PRE, data$Ebola_POST, paired = TRUE)

#evd monitoring
t.test(data$EVD_PRE, data$EVD_POST, paired = TRUE)

#idn
t.test(data$IDN_PRE, data$IDN_POST, paired = TRUE)

```

---

## Cohen's d for Each Question
```{r cohens d}
#overall score cohens d
effectsize::cohens_d(data$SCORE_PRE_PCT, data$SCORE_POST_PCT, ci = 0.95, alternative = "two.sided", paired = TRUE)

#overall score interpretation
effectsize::interpret_cohens_d(-1.44)

#ebola 101 cohens d
effectsize::cohens_d(data$Ebola_PRE, data$Ebola_POST, ci = 0.95, alternative = "two.sided", paired = TRUE)

#ebola 101 interpretation
effectsize::interpret_cohens_d(-0.93)

#evd monitoring cohens d
effectsize::cohens_d(data$EVD_PRE, data$EVD_POST, ci = 0.95, alternative = "two.sided", paired = TRUE)

#evd monitoring interpretation
effectsize::interpret_cohens_d(-0.49)

#idn cohens d
effectsize::cohens_d(data$IDN_PRE, data$IDN_POST, ci = 0.95, alternative = "two.sided", paired = TRUE)

#idn interpretation
effectsize::interpret_cohens_d(-1.29)
```


