---
title: "Quizdom Data Processing"
output:
  html_document :
    theme: flatly
    toc: FALSE
---

<br>

---

## Introduction 
This markdown conducts the data processing to prepare the Quizdom data for analysis.
    
    
The data processing will follow these steps:
1. Import graded dataframes for pre/post tests
2. Filter out participants who did not answer more than half of either the pre-test or post-test questions
3. Combine the pre/post-test data based on Participant ID & Region
4. Save processed dataset as .rds

---

## Required Packages
The following R packages are required for this script:

* here: for path setting
* readxl: for importing Excel data
* skimr: for data summarization
* tidyverse: for using all packages in the Tidyverse for data wrangling (ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, and forcats)

```{r libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load required packages
library(here) #to set the path
library(readxl) # to import Excel data
library(skimr) #to summarize data
library(tidyverse) #to use all packages in the Tidyverse for data wrangling (ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, and forcats)
```

---

## Load Data
Load the data saved in the `raw_data` folder.

```{r load data}
#define path to data
pre_location <- here::here("data", "raw_data", "Compiled_Pre_Data.xlsx")
post_location <- here::here("data", "raw_data", "Compiled_Post_Data.xlsx")

#load data
pre <- readxl::read_xlsx(pre_location, sheet = "Graded")
post <- readxl::read_xlsx(post_location, sheet = "Graded")

```

---

## Data Overview
Look at the data to ensure variables imported correctly.

```{r data overview}
#pre
summary(pre)

#post
summary(post)
```

---

## Filter Incomplete Responses
Filter out participants who did not answer more than half of either the pre-test or post-test questions

```{r filter incomplete responses}
#set threshold for a 50% cut-off
threshold <- 0.5 

#filter pre
pre_filtered <- pre %>%
                  dplyr::rowwise() %>%
                  dplyr::filter(sum(is.na(dplyr::c_across(Q1_PRE:Q14_PRE))) / length(dplyr::c_across(Q1_PRE:Q14_PRE)) <= threshold)

#filter post
post_filtered <- post %>%
                  dplyr::rowwise() %>%
                  dplyr::filter(sum(is.na(dplyr::c_across(Q1_POST:Q14_POST))) / length(dplyr::c_across(Q1_POST:Q14_POST)) <= threshold)
```

---

## Combined Dataframes
Combine the pre and post dataframes into one, based on `ParticipantID` and `Region`.

```{r combine dataframes}
#combine using an inner join to only include matched rows
data_all <- dplyr::inner_join(pre_filtered, post_filtered, by = c("Region", "ParticipantID"))

#replace NAs with 0
data_all <- replace(data_all, is.na(data_all), 0)
```

--

## Save Processed Data
Save the processed data to be referenced in subsequent analyses.
```{r save processed data}
#location to save file
data_location_save <- here::here("data", "processed_data", "processeddata.rds")

#save data as RDS
saveRDS(data_all, data_location_save)
```
